---
title: "Online Appendix -- PartialNetwork: An R package for estimating peer effects using partial network information"
author: "Vincent Boucher and Elysée Aristide Houndetoungan"
date: "`r Sys.Date()`"
output:
  pdf_document: 
    citation_package: natbib
    number_sections: yes
  bookdown::pdf_book:
    citation_package: biblatex
bibliography: ["References.bib", "Packages.bib"]
biblio-style: "apalike"
link-citations: true
urlcolor: blue
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{PartialNetwork package: Examples and Applications}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instrumental Variable (IV) procedure
We provide the function `sim.IV(dnetwork, X, y, replication, power)` where `dnetwork` is the network linking probabilities, `X` is a matrix of covariates, `y` (optional) is the vector of outcome, `replication` (optional, default = 1) is the number of replications, and `power` (optional, default = 1) is the number of powers of the interaction matrix used to generate the instruments. The function outputs a proxy for `Gy` and simulated instruments.

The following code provides an example using a sample of 30 networks of size 50 each. For the sake of the example, we assume that linking probabilities are *known* and drawn from an uniform distribution. We first simulate data. Then, we estimate the linear-in-means model using our IV procedure, using the known linking probabilities to generate approximations of the true network.

```{r IV1, echo = TRUE, eval = TRUE}
library(PartialNetwork)
set.seed(123)
# Number of groups
M             <- 30
# size of each group
N             <- rep(50,M)
# individual effects
beta          <- c(2,1,1.5) 
# endogenous effects
alpha         <- 0.4
# std-dev errors
se            <- 2 
# prior distribution
prior         <- runif(sum(N*(N-1)))
prior         <- vec.to.mat(prior, N, normalise = FALSE)
# covariates
X             <- cbind(rnorm(sum(N),0,5),rpois(sum(N),7))
# true network
G0            <- sim.network(prior)
# normalise 
G0norm        <- norm.network(G0)
# simulate dependent variable use an external package
y             <- CDatanet::simSARnet(~ X, contextual = FALSE, Glist = G0norm, 
                                     theta = c(alpha, beta, se))
y             <- y$y
# generate instruments 
instr         <- sim.IV(prior, X, y, replication = 1, power = 1)

GY1c1         <- instr[[1]]$G1y       # proxy for Gy (draw 1)
GXc1          <- instr[[1]]$G1X[,,1]  # proxy for GX (draw 1)
GXc2          <- instr[[1]]$G2X[,,1]  # proxy for GX (draw 2)
# build dataset
# keep only instrument constructed using a different draw than the one used to proxy Gy
dataset           <- as.data.frame(cbind(y, X, GY1c1, GXc1, GXc2)) 
colnames(dataset) <- c("y","X1","X2","G1y", "G1X1", "G1X2", "G2X1", "G2X2") 
```
Once the instruments are generated, the estimation can be performed using standard tools, e.g. the function `ivreg` from the **AER** package. For example, if we use the same draw for the proxy and the instruments, the estimation is "bad".

```{r IV2, echo = TRUE, eval = TRUE, message=FALSE}
library(AER)
# Same draws
out.iv1           <- ivreg(y ~ X1 + X2 + G1y | X1 + X2 + G1X1 + G1X2, data = dataset)
summary(out.iv1)
```

If we use different draws for the proxy and the instruments, the estimation is "good".

```{r IV3, echo = TRUE, eval = TRUE, message=FALSE}
# Different draws
out.iv2           <- ivreg(y ~ X1 + X2 + G1y | X1 + X2 + G2X1 + G2X2, data = dataset)
summary(out.iv2)
```

# Bayesian estimator without network formation model
The Bayesian estimator is neatly packed in the function `mcmcSAR` (see the help page of the function in the package, using `?mcmcSAR`, for more details on the function). Below, we provide a simple example using simulated data.

For the sake of the example, we assume that linking probabilities are *known* and drawn from an uniform distribution. We first simulate data. Then, we estimate the linear-in-means model using our Bayesian estimator.

For Example I-1 (`out.none1`), we assume that the network is entirely observed.

For Example I-2, we assume that only 60% of the links are observed. Estimation `out.none2.1` assumes that the sampled network is the true one (inconsistent, peer effects are overestimated). Estimation `out.none2.2` specifies which links are observed and which ones are not. The true probabilities are used to sample un-observed links (consistent).

For Example I-3, we assume that only linking probabilities are known. Estimation `out.none3.1` assumes the researcher uses a draw from that distribution as the true network (inconsistent, peer effects are overestimated). Estimation `out.none3.2` specifies that no link is observed, but that the distribution is known (consistent).

```{r BayesNone0, echo=FALSE}
load(url('https://github.com/ahoundetoungan/PartialNetwork/blob/master/datavignettes/out.none.rda?raw=true'))
# save(out.none1, out.none2.1, out.none2.2, out.none3.1, out.none3.2, file = "out.none.rda")
```

```{r BayesNone1a, eval=FALSE}
library(PartialNetwork)
set.seed(123)
# EXAMPLE I: WITHOUT NETWORK FORMATION MODEL 
# Number of groups
M             <- 50
# size of each group
N             <- rep(30,M)
# individual effects
beta          <- c(2,1,1.5) 
# contextual effects
gamma         <- c(5,-3) 
# endogenous effects
alpha         <- 0.4
# std-dev errors
se            <- 1 
# prior distribution
prior         <- runif(sum(N*(N-1)))
prior         <- vec.to.mat(prior, N, normalise = FALSE)
# covariates
X             <- cbind(rnorm(sum(N),0,5),rpois(sum(N),7))
# true network
G0            <- sim.network(prior)
# normalize 
G0norm        <- norm.network(G0)
# simulate dependent variable use an external package
y             <- CDatanet::simSARnet(~ X, contextual = TRUE, Glist = G0norm, 
                                     theta = c(alpha, beta, gamma, se))
y             <- y$y
# dataset
dataset       <- as.data.frame(cbind(y, X1 = X[,1], X2 = X[,2])) 
# Example I-1: When the network is fully observed 
out.none1     <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "all",
                         G0 = G0, data = dataset, iteration = 2e4)
```
```{r BayesNone1aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  20000 
Elapsed time           :  0  HH  0  mm  23  ss 
 
Peer effects acceptance rate: 0.44065")
```
```{r BayesNone1b}
summary(out.none1)
```
```{r BayesNone1c, fig.height = 3, fig.align = "center"}
plot(out.none1, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```
```{r BayesNone21a, eval=FALSE}
# Example I-2: When a part of the network is observed 
# 60% of the network data is observed
G0.obs       <- lapply(N, function(x) matrix(rbinom(x^2, 1, 0.6), x))
# replace the non-observed part of the network by 0 (missing links)
G0.start     <- lapply(1:M, function(x) G0[[x]]*G0.obs[[x]])
# Use network with missing data as the true network
out.none2.1  <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "all",
                        G0 = G0.start,   data = dataset, iteration = 2e4)
```
```{r BayesNone21aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  20000 
Elapsed time           :  0  HH  0  mm  23  ss 
 
Peer effects acceptance rate: 0.4317")
```
```{r BayesNone21b}
summary(out.none2.1) # the peer effets seem overestimated
```
```{r BayesNone21c, fig.height = 3, fig.align = "center"}
plot(out.none2.1, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```
```{r BayesNone22a, eval=FALSE}
out.none2.2  <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = G0.obs,
                        G0 = G0.start, data = dataset, 
                        mlinks = list(dnetwork = prior), iteration = 2e4)
```
```{r BayesNone22aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  20000 
Elapsed time           :  0  HH  41  mm  37  ss 
 
Peer effects acceptance rate: 0.4353")
```
```{r BayesNone22b}
summary(out.none2.2)
```
```{r BayesNone22c, fig.height = 3, fig.align = "center"}
plot(out.none2.2, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```
```{r BayesNone31a, eval=FALSE}
# Example I-3: When only the network distribution is available 
# Simulate a fictitious network and use as true network
G0.tmp       <- sim.network(prior)
out.none3.1  <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "all",
                        G0 = G0.tmp, data = dataset, iteration = 2e4)
```
```{r BayesNone31aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  20000 
Elapsed time           :  0  HH  0  mm  23  ss 
 
Peer effects acceptance rate: 0.44445")
```
```{r BayesNone31b}
summary(out.none3.1)  # the peer effets seem overestimated
```
```{r BayesNone31c, fig.height = 3, fig.align = "center"}
plot(out.none3.1, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```
```{r BayesNone32a, eval=FALSE}
out.none3.2  <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "none",
                        data = dataset, mlinks = list(dnetwork = prior), iteration = 2e4)
```
```{r BayesNone32aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  20000 
Elapsed time           :  1  HH  42  mm  2  ss 
 
Peer effects acceptance rate: 0.42995")
```
```{r BayesNone32b}
summary(out.none3.2)  
```
```{r BayesNone32c, fig.height = 3, fig.align = "center"}
plot(out.none3.2, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```

# Bayesian estimator with logit model as network formation model

For this example, we assume that links are generated using a simple logit model. We first simulate data. Then, we assume that the researcher only observes 60% of the links (Example II-1), but know that the network formation model is logistic.

```{r BayesLog0, echo=FALSE}
load(url('https://github.com/ahoundetoungan/PartialNetwork/blob/master/datavignettes/out.logi.rda?raw=true'))
# save(out.logi2.2, out.logi3.2, file = "out.logi.rda")
```
```{r BayesLog1a, eval=FALSE}
# EXAMPLE II: NETWORK FORMATION MODEL: LOGIT 
library(PartialNetwork)
set.seed(123)
# Number of groups
M             <- 50
# size of each group
N             <- rep(30,M)
# individual effects
beta          <- c(2,1,1.5) 
# contextual effects
gamma         <- c(5,-3) 
# endogenous effects
alpha         <- 0.4
# std-dev errors
se            <- 2 
# parameters of the network formation model
rho           <- c(-2, -.5, .2)
# covariates
X             <- cbind(rnorm(sum(N),0,5),rpois(sum(N),7))
# compute distance between individuals 
tmp           <- c(0, cumsum(N))
X1l           <- lapply(1:M, function(x) X[c(tmp[x] + 1):tmp[x+1],1])
X2l           <- lapply(1:M, function(x) X[c(tmp[x] + 1):tmp[x+1],2])
dist.net      <- function(x, y) abs(x - y) 
X1.mat        <- lapply(1:M, function(m) {
  matrix(kronecker(X1l[[m]], X1l[[m]], FUN = dist.net), N[m])})
X2.mat        <- lapply(1:M, function(m) {
  matrix(kronecker(X2l[[m]], X2l[[m]], FUN = dist.net), N[m])})
# true network
covar         <- as.matrix(cbind("Const" = 1, 
                                 "dX1"   = mat.to.vec(X1.mat), 
                                 "dX2"   = mat.to.vec(X2.mat)))
ynet          <- covar %*% rho
ynet          <- 1*((ynet + rlogis(length(ynet))) > 0)
G0            <- vec.to.mat(ynet, N, normalise = FALSE)
G0norm        <- norm.network(G0)
# simulate dependent variable use an external package
y             <- CDatanet::simSARnet(~ X, contextual = TRUE, Glist = G0norm, 
                                     theta = c(alpha, beta, gamma, se))
y             <- y$y
# dataset
dataset       <- as.data.frame(cbind(y, X1 = X[,1], X2 = X[,2])) 
```

```{r BayesLog21a, eval=FALSE}
# Example II-1: When a part of the network is observed 
# 60% of the network data is observed
G0.obs       <- lapply(N, function(x) matrix(rbinom(x^2, 1, 0.6), x))
# replace the non-observed part of the network by 0
G0.start     <- lapply(1:M, function(x) G0[[x]]*G0.obs[[x]])
# Infer the missing links in the network data
mlinks       <- list(model = "logit", mlinks.formula = ~ dX1 + dX2, 
                     mlinks.data = as.data.frame(covar))
out.logi2.2  <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = G0.obs,
                        G0 = G0.start, data = dataset, mlinks = mlinks, 
                        iteration = 2e4)
```
```{r BayesLog22aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY*************
Number of group        :  50
Iteration              :  20000
Elapsed time           :  0  HH  33  mm  1  ss

Peer effects acceptance rate: 0.438
rho acceptance rate         : 0.27185")
```
```{r BayesLog22b}
summary(out.logi2.2) 
```
```{r BayesLog22c, fig.height = 3, fig.align = "center"}
plot(out.logi2.2, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```
```{r BayesLog22cc, fig.height = 3, fig.align = "center"}
plot(out.logi2.2, plot.type = "sim", which.parms = "rho", mar = c(3, 2.1, 1, 1))
```

Example II-2 disregards the information about observed links (which we used to estimate the logit model) and only uses the asymptotic distribution of the network formation parameters.

```{r BayesLog31a, eval=FALSE}
# Example II-2: When only the network distribution is available
# Infer the network data
# We only provide estimate of rho and its variance
Gvec         <- mat.to.vec(G0, ceiled = TRUE)
logestim     <- glm(Gvec ~ -1 + covar, family = binomial(link = "logit"))
slogestim    <- summary(logestim)
estimates    <- list("rho"     = logestim$coefficients, 
                     "var.rho" = slogestim$cov.unscaled,
                     "N"       = N)
mlinks       <- list(model = "logit", mlinks.formula = ~ dX1 + dX2, 
                     mlinks.data = as.data.frame(covar), estimates = estimates)
out.logi3.2  <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "none", 
                        data = dataset, mlinks = mlinks, iteration = 2e4)
```

```{r BayesLog32aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  20000 
Elapsed time           :  1  HH  20  mm  2  ss 
 
Peer effects acceptance rate: 0.4446
rho acceptance rate         : 0.27905")
```
```{r BayesLog32b}
summary(out.logi3.2) 
```
```{r BayesLog32c, fig.height = 3, fig.align = "center"}
plot(out.logi3.2, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```

```{r BayesLog32cc, fig.height = 3, fig.align = "center"}
plot(out.logi3.2, plot.type = "sim", which.parms = "rho", mar = c(3, 2.1, 1, 1))

```

# Bayesian estimator with latent space model as network formation model
## ARD, @breza2020using

We also offer a function of the estimator in @breza2020using. We first simulate data. We then estimate the model's parameters assuming that the researcher only knows ARD. We present two examples, one for which we observe ARD for the entire population (Example 1) and one for which we observe ARD for only 70% of the population (Example 2).

```{r Bayesard0, echo=FALSE}
load(url('https://github.com/ahoundetoungan/PartialNetwork/blob/master/datavignettes/out.ard.rda?raw=true'))
# save(data.plot1, data.plot2, genz, genv, zi, vk, file = "out.ard.rda")
```

The data is simulated following a procedure similar to the one in @breza2020using. 
```{r ard1, eval=FALSE}
library(PartialNetwork)
set.seed(123)
# LATENT SPACE MODEL 
N           <- 500
genzeta     <- 1
mu          <- -1.35
sigma       <- 0.37
K           <- 12    # number of traits
P           <- 3     # Sphere dimension 
# ARD parameters
# Generate z (spherical coordinates)
genz        <- rvMF(N, rep(0,P))
# Generate nu  from a Normal(mu, sigma^2) (The gregariousness)
gennu       <- rnorm(N, mu, sigma)
# compute degrees
gend        <- N*exp(gennu)*exp(mu+0.5*sigma^2)*exp(logCpvMF(P,0) - logCpvMF(P,genzeta))
# Link probabilities
Prior       <- sim.dnetwork(gennu, gend, genzeta, genz) 
# Adjacency matrix
G           <- sim.network(Prior)
# Generate vk, the trait location
genv        <- rvMF(K, rep(0, P))
# set fixed some vk  distant
genv[1,]    <- c(1, 0, 0)
genv[2,]    <- c(0, 1, 0)
genv[3,]    <- c(0, 0, 1)
# eta, the intensity parameter
geneta      <- abs(rnorm(K, 2, 1))
# Build traits matrix
densityatz  <- matrix(0, N, K)
for(k in 1:K){
  densityatz[,k] <- dvMF(genz, genv[k,]*geneta[k])
}
trait       <- matrix(0, N, K)
NK          <- floor(runif(K, 0.8, 0.95)*colSums(densityatz)/apply(densityatz, 2, max))
for (k in 1:K) {
  trait[,k] <- rbinom(N, 1, NK[k]*densityatz[,k]/sum(densityatz[,k]))
}
# Build ADR
ARD         <- G %*% trait
# generate b
genb        <- numeric(K)
for(k in 1:K){
  genb[k]   <- sum(G[,trait[,k]==1])/sum(G)
}
```
```{r ard1a, eval=FALSE}
# Example1: ARD is observed for the whole population
# initialization 
d0     <- exp(rnorm(N)); b0 <- exp(rnorm(K)); eta0 <- rep(1,K)
zeta0  <- 2; z0 <- matrix(rvMF(N, rep(0,P)), N); v0 <- matrix(rvMF(K,rep(0, P)), K)
# We should fix some vk and bk
vfixcolumn      <- 1:5
bfixcolumn      <- c(3, 7, 9)
b0[bfixcolumn]  <- genb[bfixcolumn]
v0[vfixcolumn,] <- genv[vfixcolumn,]
start           <- list("z" = z0, "v" = v0, "d" = d0, "b" = b0, "eta" = eta0, 
                        "zeta" = zeta0)
# MCMC
estim.ard1      <- mcmcARD(Y = ARD, traitARD = trait, start = start, fixv = vfixcolumn,
                           consb = bfixcolumn, iteration = 5000)  
```
```{r arda, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

********SUMMARY******** 
n              :  500 
K              :  12 
Dimension      :  3 
Iteration      :  5000 
Elapsed time   :  0  HH  1  mm  18  ss 
 
Average acceptance rate 
                      z:  0.441398 
                      d:  0.4399204 
                      b:  0.4392833 
                    eta:  0.4397833 
                   zeta:  0.4402")
```
```{r ardaa1, eval=FALSE}
# plot coordinates of individual 123
i     <- 123
zi    <- estim.ard1$simulations$z[i,,]
par(mfrow = c(3, 1), mar = c(2.1, 2.1, 1, 1))
invisible(lapply(1:3, function(x) {
  plot(zi[x,], type = "l", ylab = "", col = "blue", ylim = c(-1, 1))
  abline(h = genz[i, x], col = "red")
}))
```

```{r ardaa1a, echo=FALSE, fig.height = 4, fig.align = "center"}
i     <- 123
par(mfrow = c(3, 1), mar = c(2.1, 2.1, 1, 1))
invisible(lapply(1:3, function(x) {
  plot(zi[x,], type = "l", ylab = "", col = "blue", ylim = c(-1, 1))
  abline(h = genz[i, x], col = "red")
}))
```

```{r ardaa2, eval=FALSE}
# plot coordinates of traits 8
k     <- 8
vk    <- estim.ard1$simulations$v[k,,]
par(mfrow = c(3, 1), mar = c(2.1, 2.1, 1, 1))
invisible(lapply(1:3, function(x) {
  plot(vk[x,], type = "l", ylab = "", col = "blue", ylim = c(-1, 1))
  abline(h = genv[k, x], col = "red")
}))
```

```{r ardaa2a, echo=FALSE, fig.height = 4, fig.align = "center"}
k     <- 8
par(mfrow = c(3, 1), mar = c(2.1, 2.1, 1, 1))
invisible(lapply(1:3, function(x) {
  plot(vk[x,], type = "l", ylab = "", col = "blue", ylim = c(-1, 1))
  abline(h = genv[k, x], col = "red")
}))
```

```{r ardb, message=FALSE, eval=FALSE}
# plot degree
library(ggplot2)
data.plot1 <- data.frame(True_degree  = gend, 
                         Estim_degree = colMeans(tail(estim.ard1$simulations$d, 2500)))
ggplot(data = data.plot1, aes(x = True_degree, y = Estim_degree)) + 
   geom_abline(col = "red") + geom_point(col = "blue")
```
```{r ardbb, message=FALSE, echo=FALSE, fig.height = 3, fig.align = "center"}
library(ggplot2)
ggplot(data = data.plot1, aes(x = True_degree, y = Estim_degree)) + 
   geom_abline(col = "red") + geom_point(col = "blue")
```

```{r ard2a, eval=FALSE}
# Example2: ARD is observed for 70% population
# sample with ARD 
n          <- round(0.7*N)
# individual with ARD
iselect    <- sort(sample(1:N, n, replace = FALSE))
ARDs       <- ARD[iselect,]
traits     <- trait[iselect,]
# initialization 
d0         <- d0[iselect]; z0 <- z0[iselect,] 
start      <- list("z" = z0, "v" = v0, "d" = d0, "b" = b0, "eta" = eta0, "zeta" = zeta0)
# MCMC
estim.ard2 <- mcmcARD(Y = ARDs, traitARD = traits, start = start, fixv = vfixcolumn,
                      consb = bfixcolumn, iteration = 5000)  
```
```{r ardc, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

********SUMMARY******** 
n              :  350 
K              :  12 
Dimension      :  3 
Iteration      :  5000 
Elapsed time   :  0  HH  0  mm  52  ss 
 
Average acceptance rate 
                      z:  0.4419703 
                      d:  0.4401291 
                      b:  0.4406667 
                    eta:  0.44055 
                   zeta:  0.4422")
```
```{r ard2b, eval=FALSE}
# estimation for non ARD
# we need a logical vector indicating if the i-th element has ARD
hasARD      <- (1:N) %in% iselect
# we use the matrix of traits to estimate distance between individuals
estim.nard2 <- fit.dnetwork(estim.ard2, X = trait, obsARD = hasARD, m = 1) 
```
```{r ardd, echo=FALSE}
cat("ARD non observed on the entire population 
0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

Average link probabilities estimated 
Iteration             : 2500 
Elapsed time          : 0  HH  0  mm  13  ss ")
```
```{r arde, eval=FALSE}
# estimated degree
estd          <- estim.nard2$degree
data.plot2    <- data.frame(True_degree  = gend, 
                            Estim_degree = estd, 
                            Has_ARD      = ifelse(hasARD, "YES", "NO"))
ggplot(data = data.plot2, aes(x = True_degree, y = Estim_degree, colour = Has_ARD)) + 
  geom_abline(col = "red") + geom_point() 
```
```{r ardee, message=FALSE, echo=FALSE, fig.height = 3, fig.align = "center"}
ggplot(data = data.plot2, aes(x = True_degree, y = Estim_degree, colour = Has_ARD)) + 
  geom_abline(col = "red") + geom_point() 
```

## Estimating peer effects model with ARD

Given the predicted probabilities, estimated using the estimator proposed by @breza2020using assuming that ARD are observed for the entire population, we implement our Bayesian estimator assuming that the posterior distribution of the linking probabilities are jointly normally distributed.

```{r Bayesard00, echo=FALSE}
load(url('https://github.com/ahoundetoungan/PartialNetwork/blob/master/datavignettes/out.lsp.rda?raw=true'))
#save(out.lspa1, out.lspa2, file = "PartialNetwork/datavignettes/out.lsp.rda")
```
```{r bayesard1, eval=FALSE}
library(PartialNetwork)
set.seed(123)
M             <- 30
N             <- rep(60, M)
genzeta       <- 3
mu            <- -1.35
sigma         <- 0.37
K             <- 12    # number of traits
P             <- 3     # Sphere dimension 
# In this loop, we generate data for the latent space model and 
# estimate the latent space model in the M sub-networks
estimates     <- list()
list.trait    <- list()
prior         <- list()
G0            <- list()
for (m in 1:M) {
  # ARD parameters
  # Generate z (spherical coordinates)
  genz    <- rvMF(N[m], rep(0,P))
  # Generate nu  from a Normal(mu, sigma^2) (The gregariousness)
  gennu   <- rnorm(N[m],mu,sigma)
  # compute degrees
  gend    <- N[m]*exp(gennu)*exp(mu+0.5*sigma^2)*exp(logCpvMF(P,0) - logCpvMF(P,genzeta))
  # Link probabilities
  Probabilities <- sim.dnetwork(gennu, gend, genzeta, genz) 
  prior[[m]]    <- Probabilities
  # Adjacency matrix
  G        <- sim.network(Probabilities)
  G0[[m]]  <- G
  # Generate vk, the trait location
  genv     <- rvMF(K, rep(0, P))
  # set fixed some vk  distant
  genv[1,] <- c(1, 0, 0)
  genv[2,] <- c(0, 1, 0)
  genv[3,] <- c(0, 0, 1)
  # eta, the intensity parameter
  geneta   <-abs(rnorm(K, 2, 1))
  # Build traits matrix
  densityatz       <- matrix(0, N[m], K)
  for(k in 1:K){
    densityatz[,k] <- dvMF(genz, genv[k,]*geneta[k])
  }
  trait       <- matrix(0, N[m], K)
  NK          <- floor(runif(K, .8, .95)*colSums(densityatz)/apply(densityatz, 2, max))
  for (k in 1:K) {
    trait[,k] <- rbinom(N[m], 1, NK[k]*densityatz[,k]/sum(densityatz[,k]))
  }
  list.trait[[m]]  <- trait
  # Build ADR
  ARD         <- G %*% trait
  # generate b
  genb        <- numeric(K)
  for(k in 1:K){
    genb[k]  <- sum(G[,trait[,k]==1])/sum(G) + 1e-8
  }
  
  # initialization 
  d0     <- gend; b0 <- exp(rnorm(K)); eta0 <- rep(1,K); zeta0 <- genzeta 
  z0     <- matrix(rvMF(N[m], rep(0,P)), N[m]); v0 <- matrix(rvMF(K,rep(0, P)), K)
  # We should fix some vk and bk
  vfixcolumn      <- 1:5
  bfixcolumn      <- c(1, 3, 5, 7, 9, 11)
  b0[bfixcolumn]  <- genb[bfixcolumn]
  v0[vfixcolumn,] <- genv[vfixcolumn,]
  start           <- list("z" = z0, "v" = v0, "d" = d0, "b" = b0, "eta" = eta0, 
                          "zeta" = zeta0)
  # MCMC
  estimates[[m]]  <- mcmcARD(Y = ARD, traitARD = trait, start = start, fixv = vfixcolumn, 
                             consb = bfixcolumn, sim.d = FALSE, sim.zeta = FALSE, 
                             iteration = 5000, ctrl.mcmc = list(print = FALSE))
}
## Simulate X and y
# individual effects
beta          <- c(2,1,1.5) 
# contextual effects
gamma         <- c(5,-3) 
# endogenous effects
alpha         <- 0.4
# std-dev errors
se            <- 1
# covariates
X             <- cbind(rnorm(sum(N),0,5),rpois(sum(N),7))
# Normalise G0
G0norm        <- norm.network(G0)
# simulate dependent variable use an external package
y             <- CDatanet::simSARnet(~ X, contextual = TRUE, Glist = G0norm, 
                                     theta = c(alpha, beta, gamma, se))
y             <- y$y
# dataset
dataset       <- as.data.frame(cbind(y, X1 = X[,1], X2 = X[,2])) 
```
```{r bayesard2, eval=FALSE}
mlinks       <- list(model = "latent space", estimates = estimates)
out.lspa1    <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "none", 
                        data = dataset, mlinks = mlinks, iteration = 2e4)
```
```{r Bayesarda, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  30 
Iteration              :  20000 
Elapsed time           :  7  HH  49  mm  17  ss 
 
Peer effects acceptance rate: 0.43145
rho acceptance rate         : 0.2697867")
```

```{r Bayesard2b}
summary(out.lspa1) 
```
```{r Bayesard2c, fig.height = 3, fig.align = "center"}
plot(out.lspa1, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```


## Estimating peer effects with partial ARD

Given the predicted probabilities, estimated using the estimator proposed by @breza2020using assuming that ARD are observed for 70% $\sim$ 100% of the population, we implement our Bayesian estimator assuming that the posterior distribution of the linking probabilities are jointly normally distributed.


```{r bayesard3, eval=FALSE}
library(PartialNetwork)
set.seed(123)
M             <- 30
N             <- rep(60, M)
genzeta       <- 3
mu            <- -1.35
sigma         <- 0.37
K             <- 12
P             <- 3
# In this loop, we generate data for the latent space model and 
# estimate the latent space model in the M sub-networks
estimates     <- list()
list.trait    <- list()
obARD         <- list()
prior         <- list()
G0            <- list()
for (m in 1:M) {
  # ARD parameters
  # Generate z (spherical coordinates)
  genz    <- rvMF(N[m], rep(0,P))
  # Generate nu  from a Normal(mu, sigma^2) (The gregariousness)
  gennu   <- rnorm(N[m],mu,sigma)
  # compute degrees
  gend    <- N[m]*exp(gennu)*exp(mu+0.5*sigma^2)*exp(logCpvMF(P,0) - logCpvMF(P,genzeta))
  # Link probabilities
  Probabilities <- sim.dnetwork(gennu, gend, genzeta, genz) 
  prior[[m]]    <- Probabilities
  # Adjacency matrix
  G        <- sim.network(Probabilities)
  G0[[m]]  <- G
  # Generate vk, the trait location
  genv     <- rvMF(K, rep(0, P))
  # set fixed some vk  distant
  genv[1,] <- c(1, 0, 0)
  genv[2,] <- c(0, 1, 0)
  genv[3,] <- c(0, 0, 1)
  # eta, the intensity parameter
  geneta   <-abs(rnorm(K, 2, 1))
  # Build traits matrix
  densityatz  <- matrix(0, N[m], K)
  for(k in 1:K){
    densityatz[,k] <- dvMF(genz, genv[k,]*geneta[k])
  }
  trait       <- matrix(0, N[m], K)
  NK          <- floor(runif(K, .8, .95)*colSums(densityatz)/apply(densityatz, 2, max)) 
  for (k in 1:K) {
    trait[,k] <- rbinom(N[m], 1, NK[k]*densityatz[,k]/sum(densityatz[,k]))
  } 
  list.trait[[m]]  <- trait
  # Build ADR
  ARD         <- G %*% trait
  # generate b
  genb        <- numeric(K)
  for(k in 1:K){
    genb[k]  <- sum(G[,trait[,k]==1])/sum(G) + 1e-8
  }
  # sample with ARD 
  n          <- round(runif(1, .7, 1)*N[m])
  # individual with ARD
  iselect    <- sort(sample(1:N[m], n, replace = FALSE))
  hasARD     <- (1:N[m]) %in% iselect
  obARD[[m]] <- hasARD
  ARDs       <- ARD[iselect,]
  traits     <- trait[iselect,]
  # initialization 
  d0         <- gend[iselect]; b0 <- exp(rnorm(K)); eta0 <- rep(1,K); zeta0 <- genzeta
  z0         <- matrix(rvMF(n, rep(0,P)), n); v0 <- matrix(rvMF(K, rep(0, P)), K) 
  # We should fix some vk and bk
  vfixcolumn      <- 1:5
  bfixcolumn      <- c(1, 3, 5, 7, 9, 11)
  b0[bfixcolumn]  <- genb[bfixcolumn]
  v0[vfixcolumn,] <- genv[vfixcolumn,]
  start           <- list("z" = z0, "v" = v0, "d" = d0, "b" = b0, "eta" = eta0, 
                          "zeta" = zeta0)
  # MCMC
  estimates[[m]]  <- mcmcARD(Y = ARDs, traitARD = traits, start = start, fixv = vfixcolumn, 
                             consb = bfixcolumn,  sim.d = FALSE, sim.zeta = FALSE, 
                             iteration = 5000, ctrl.mcmc = list(print = FALSE))
}
## Simulate X and y
# individual effects
beta          <- c(2,1,1.5) 
# contextual effects
gamma         <- c(5,-3) 
# endogenous effects
alpha         <- 0.4
# std-dev errors
se            <- 1
# covariates
X             <- cbind(rnorm(sum(N),0,5),rpois(sum(N),7))
# Normalise G0
G0norm        <- norm.network(G0)
# simulate dependent variable use an external package
y             <- CDatanet::simSARnet(~ X, contextual = TRUE, Glist = G0norm, 
                                     theta = c(alpha, beta, gamma, se))
y             <- y$y
# dataset
dataset       <- as.data.frame(cbind(y, X1 = X[,1], X2 = X[,2])) 
```
```{r bayesard4, eval=FALSE}
mlinks       <- list(model = "latent space", estimates = estimates,
                     mlinks.data = list.trait, obsARD = obARD)
out.lspa2    <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "none", 
                        data = dataset, mlinks = mlinks, iteration = 2e4)

```

```{r Bayesard4a, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  30 
Iteration              :  20000 
Elapsed time           :  7  HH  51  mm  0  ss 
 
Peer effects acceptance rate: 0.44075
rho acceptance rate         : 0.2705733")
```

```{r Bayesard4b}
summary(out.lspa2)
```
```{r Bayesard4c, fig.height = 3, fig.align = "center"}
plot(out.lspa2, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```
