---
title: "PartialNetwork: An R package for estimating peer effects using partial network information"
author: "Vincent Boucher and Elysée Aristide Houndetoungan"
date: "`r Sys.Date()`"
output:
  pdf_document: 
    citation_package: natbib
    number_sections: yes
  bookdown::pdf_book:
    citation_package: biblatex
bibliography: ["References.bib", "Packages.bib"]
biblio-style: "apalike"
link-citations: true
urlcolor: blue
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{PartialNetwork package: Examples and Applications}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instrumental Variable procedure
We provide the function `sim.IV(dnetwork, X, y, replication, power)` where `dnetwork` is the network linking probabilities, `X` is a matrix of covariates, `y` (optional) is the vector of outcome, `replication` (optional, default = 1) is the number of replication, and `power` (optional, default = 1) is the number of powers of the interaction matrix used to generate the instruments. The function outputs a proxy for `Gy` and simulated instruments. The following code provides an example using a single group of network.

```{r IV1, echo = TRUE, eval = TRUE}
library(PartialNetwork)
set.seed(123)
# Number of groups
M             <- 30
# size of each group
N             <- rep(50,M)
# individual effects
beta          <- c(2,1,1.5) 
# endogenous effects
alpha         <- 0.4
# std-dev errors
se            <- 2 
# prior distribution
prior         <- runif(sum(N*(N-1)))
prior         <- vec.to.mat(prior, N, normalise = FALSE)
# covariates
X             <- cbind(rnorm(sum(N),0,5),rpois(sum(N),7))
# true network
G0            <- sim.network(prior)
# normalise 
G0norm        <- norm.network(G0)
# simulate dependent variable use an external package
y             <- CDatanet::simSARnet(~ X, contextual = FALSE, Glist = G0norm, 
                                     theta = c(alpha, beta, se))
y             <- y$y
# generate instruments 
instr         <- sim.IV(prior, X, y, replication = 1, power = 1)

GY1c1         <- instr[[1]]$G1y       # proxy for Gy (draw 1)
GXc1          <- instr[[1]]$G1X[,,1]  # proxy for GX (draw 1)
GXc2          <- instr[[1]]$G2X[,,1]  # proxy for GX (draw 2)
# build dataset
# keep only instrument constructed using a different draw than the one used to proxy Gy
dataset           <- as.data.frame(cbind(y, X, GY1c1, GXc1, GXc2)) 
colnames(dataset) <- c("y","X1","X2","G1y", "G1X1", "G1X2", "G2X1", "G2X2") 
```
Once the instruments are generated, the estimation can be performed using standard tools, e.g. the function ivreg from the *AER* package. For example:
```{r IV2, echo = TRUE, eval = TRUE, message=FALSE}
library(AER)
# Same draws
out.iv1           <- ivreg(y ~ X1 + X2 + G1y | X1 + X2 + G1X1 + G1X2, data = dataset)
summary(out.iv1)
```


```{r IV3, echo = TRUE, eval = TRUE, message=FALSE}
# Different draws
out.iv2           <- ivreg(y ~ X1 + X2 + G1y | X1 + X2 + G2X1 + G2X2, data = dataset)
summary(out.iv2)
```

# Bayesian estimator without network formation model
The Bayesian estimator is neatly packed in the function `mcmcSAR`. Below, we provide a simple example using simulated data.

```{r BayesNone0, echo=FALSE}
load(url('https://github.com/ahoundetoungan/PartialNetwork/blob/master/datavignettes/out.none.rda?raw=true'))
```

```{r BayesNone1a, eval=FALSE}
library(PartialNetwork)
set.seed(123)
# EXAMPLE I: WITHOUT NETWORK FORMATION MODEL 
# Number of groups
M             <- 50
# size of each group
N             <- rep(30,M)
# individual effects
beta          <- c(2,1,1.5) 
# contextual effects
gamma         <- c(5,-3) 
# endogenous effects
alpha         <- 0.4
# std-dev errors
se            <- 1 
# prior distribution
prior         <- runif(sum(N*(N-1)))
prior         <- vec.to.mat(prior, N, normalise = FALSE)
# covariates
X             <- cbind(rnorm(sum(N),0,5),rpois(sum(N),7))
# true network
G0            <- sim.network(prior)
# normalize 
G0norm        <- norm.network(G0)
# simulate dependent variable use an external package
y             <- CDatanet::simSARnet(~ X, contextual = TRUE, Glist = G0norm, 
                                     theta = c(alpha, beta, gamma, se))
y             <- y$y
# dataset
dataset       <- as.data.frame(cbind(y, X1 = X[,1], X2 = X[,2])) 
# Example I-1: When the network is fully observed 
out.none1     <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "all",
                         G0 = G0, data = dataset, iteration = 1e4)
```
```{r BayesNone1aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  10000 
Elapsed time           :  0  HH  0  mm  19  ss 
 
Peer effects acceptance rate: 0.4408")
```
```{r BayesNone1b}
summary(out.none1)
```
```{r BayesNone1c, fig.height = 3, fig.align = "center"}
plot(out.none1, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```
```{r BayesNone21a, eval=FALSE}
# Example I-2: When a part of the network is observed 
# 60% of the network data is observed
G0.obs       <- lapply(N, function(x) matrix(rbinom(x^2, 1, 0.6), x))
# replace the non-observed part of the network by 0 (missing links)
G0.start     <- lapply(1:M, function(x) G0[[x]]*G0.obs[[x]])
# Use network with missing data as the true network
out.none2.1  <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "all",
                        G0 = G0.start,   data = dataset, iteration = 1e4)
```
```{r BayesNone21aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  10000 
Elapsed time           :  0  HH  0  mm  19  ss 
 
Peer effects acceptance rate: 0.4279")
```
```{r BayesNone21b}
summary(out.none2.1) # the peer effets seem overestimated
```
```{r BayesNone21c, fig.height = 3, fig.align = "center"}
plot(out.none2.1, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```
```{r BayesNone22a, eval=FALSE}
out.none2.2  <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = G0.obs,
                        G0 = G0.start,   data = dataset, 
                        mlinks = list(dnetwork = prior), iteration = 1e4)
```
```{r BayesNone22aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  10000 
Elapsed time           :  0  HH  14  mm  39  ss 
 
Peer effects acceptance rate: 0.4391")
```
```{r BayesNone22b}
summary(out.none2.2)
```
```{r BayesNone22c, fig.height = 3, fig.align = "center"}
plot(out.none2.2, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```
```{r BayesNone31a, eval=FALSE}
# Example I-3: When only the network distribution is available 
# Simulate a fictitious network and use as true network
G0.tmp       <- sim.network(prior)
out.none3.1  <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "all",
                        G0 = G0.tmp, data = dataset, iteration = 1e4)
```
```{r BayesNone31aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  10000 
Elapsed time           :  0  HH  0  mm  17  ss 
 
Peer effects acceptance rate: 0.4485")
```
```{r BayesNone31b}
summary(out.none3.1)  # the peer effets seem overestimated
```
```{r BayesNone31c, fig.height = 3, fig.align = "center"}
plot(out.none3.1, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```
```{r BayesNone32a, eval=FALSE}
out.none3.2  <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "none",
                        data = dataset, mlinks = list(dnetwork = prior), iteration = 1e4)
```
```{r BayesNone32aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  10000 
Elapsed time         :  0  HH  35  mm  13  ss 
 
Peer effects acceptance rate: 0.4398")
```
```{r BayesNone32b}
summary(out.none3.2)  
```
```{r BayesNone32c, fig.height = 3, fig.align = "center"}
plot(out.none3.2, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```

# Bayesian estimator with logit model as network formation model
```{r BayesLog0, echo=FALSE}
load(url('https://github.com/ahoundetoungan/PartialNetwork/blob/master/datavignettes/out.logi.rda?raw=true'))
```
```{r BayesLog1a, eval=FALSE}
# EXAMPLE II: NETWORK FORMATION MODEL: LOGIT 
library(PartialNetwork)
set.seed(123)
# Number of groups
M             <- 50
# size of each group
N             <- rep(30,M)
# individual effects
beta          <- c(2,1,1.5) 
# contextual effects
gamma         <- c(5,-3) 
# endogenous effects
alpha         <- 0.4
# std-dev errors
se            <- 2 
# parameters of the network formation model
rho           <- c(-2, -.5, .2)
# covariates
X             <- cbind(rnorm(sum(N),0,5),rpois(sum(N),7))
# compute distance between individuals 
tmp           <- c(0, cumsum(N))
X1l           <- lapply(1:M, function(x) X[c(tmp[x] + 1):tmp[x+1],1])
X2l           <- lapply(1:M, function(x) X[c(tmp[x] + 1):tmp[x+1],2])
dist.net      <- function(x, y) abs(x - y) 
X1.mat        <- lapply(1:M, function(m) {
  matrix(kronecker(X1l[[m]], X1l[[m]], FUN = dist.net), N[m])})
X2.mat        <- lapply(1:M, function(m) {
  matrix(kronecker(X2l[[m]], X2l[[m]], FUN = dist.net), N[m])})
# true network
covar         <- as.matrix(cbind("Const" = 1, 
                                 "dX1"   = mat.to.vec(X1.mat), 
                                 "dX2"   = mat.to.vec(X2.mat)))
ynet          <- covar %*% rho
ynet          <- 1*((ynet + rlogis(length(ynet))) > 0)
G0            <- vec.to.mat(ynet, N, normalise = FALSE)
G0norm        <- norm.network(G0)
# simulate dependent variable use an external package
y             <- CDatanet::simSARnet(~ X, contextual = TRUE, Glist = G0norm, 
                                     theta = c(alpha, beta, gamma, se))
y             <- y$y
# dataset
dataset       <- as.data.frame(cbind(y, X1 = X[,1], X2 = X[,2])) 
```

```{r BayesLog21a, eval=FALSE}
# Example II-1: When a part of the network is observed 
# 60% of the network data is observed
G0.obs       <- lapply(N, function(x) matrix(rbinom(x^2, 1, 0.6), x))
# replace the non-observed part of the network by 0
G0.start     <- lapply(1:M, function(x) G0[[x]]*G0.obs[[x]])
# Infer the missing links in the network data
out.logi2.2  <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = G0.obs,
                        G0 = G0.start,   data = dataset, 
                        mlinks = list(model = "logit", covariates = covar), 
                        iteration = 2e4)
```
```{r BayesLog22aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  20000 
Elapsed time           :  0  HH  31  mm  41  ss 
 
Peer effects acceptance rate: 0.438
rho acceptance rate         : 0.27185")
```
```{r BayesLog22b}
summary(out.logi2.2) 
```
```{r BayesLog22c, fig.height = 3, fig.align = "center"}
plot(out.logi2.2, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```
```{r BayesLog22cc, fig.height = 3, fig.align = "center"}
plot(out.logi2.2, plot.type = "sim", which.parms = "rho", mar = c(3, 2.1, 1, 1))
```




```{r BayesLog31a, eval=FALSE}
# Example II-2: When only the network distribution is available
# Infer the network data
# We only provide estimate of rho and its variance
Gvec         <- mat.to.vec(G0, ceiled = TRUE)
logestim     <- glm(Gvec ~ -1 + covar, family = binomial(link = "logit"))
slogestim    <- summary(logestim)
estimates    <- list("rho"     = logestim$coefficients, 
                     "var.rho" = slogestim$cov.unscaled,
                     "N"       = N)
mlinks       <- list(model = "logit", covariates = covar, estimates = estimates)
out.logi3.2  <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "none", 
                        data = dataset, mlinks = mlinks, iteration = 2e4)
```

```{r BayesLog32aa, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  20000 
Elapsed time           :  1  HH  18  mm  54  ss 
 
Peer effects acceptance rate: 0.4446
rho acceptance rate         : 0.27905")
```
```{r BayesLog32b}
summary(out.logi3.2) 
```
```{r BayesLog32c, fig.height = 3, fig.align = "center"}
plot(out.logi3.2, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```

```{r BayesLog32cc, fig.height = 3, fig.align = "center"}
plot(out.logi3.2, plot.type = "sim", which.parms = "rho", mar = c(3, 2.1, 1, 1))

```

# Bayesian estimator with latent space model as network formation model
## ARD, @breza2020using
```{r Bayesard0, echo=FALSE}
load(url('https://github.com/ahoundetoungan/PartialNetwork/blob/master/datavignettes/out.ard.rda?raw=true'))
```

The data is simulated following a procedure similar to the one in @breza2020using. 
```{r ard1, eval=FALSE}
library(PartialNetwork)
set.seed(123)
# LATENT SPACE MODEL 
N           <- 500
genzeta     <- 1
mu          <- -1.35
sigma       <- 0.37
K           <- 12    # number of traits
P           <- 3     # Sphere dimension 
# ARD parameters
# Generate z (spherical coordinates)
genz        <- rvMF(N, rep(0,P))
# Generate nu  from a Normal(mu, sigma^2) (The gregariousness)
gennu       <- rnorm(N, mu, sigma)
# compute degrees
gend        <- N*exp(gennu)*exp(mu+0.5*sigma^2)*exp(logCpvMF(P,0) - logCpvMF(P,genzeta))
# Link probabilities
Prior       <- sim.dnetwork(gennu, gend, genzeta, genz) 
# Adjacency matrix
G           <- sim.network(Prior)
# Generate vk, the trait location
genv        <- rvMF(K, rep(0, P))
# set fixed some vk  distant
genv[1,]    <- c(1, 0, 0)
genv[2,]    <- c(0, 1, 0)
genv[3,]    <- c(0, 0, 1)
# eta, the intensity parameter
geneta      <- abs(rnorm(K, 2, 1))
# Build traits matrix
densityatz  <- matrix(0, N, K)
for(k in 1:K){
  densityatz[,k] <- dvMF(genz, genv[k,]*geneta[k])
}
trait            <- matrix(0, N, K)
for(k in 1:K){
  tmp       <- exp(geneta[k] + logCpvMF(3, geneta[k]))
  trait[,k] <- runif(N, 0.5*tmp, tmp) < densityatz[,k]
}
# Build ADR
ARD         <- G %*% trait
# generate b
genb        <- numeric(K)
for(k in 1:K){
  genb[k]   <- sum(G[,trait[,k]==1])/sum(G)
}
```
```{r ard1a, eval=FALSE}
# Example1: ARD is observed for the whole population
# initialization 
d0     <- exp(rnorm(N)); b0 <- exp(rnorm(K)); eta0 <- rep(1,K);
zeta0  <- 2; z0 <- matrix(rvMF(N, rep(0,P)), N); v0 <- matrix(rvMF(K,rep(0, P)), K)
# We should fix some vk and bk
vfixcolumn      <- 1:5
bfixcolumn      <- c(3, 7, 9)
b0[bfixcolumn]  <- genb[bfixcolumn]
v0[vfixcolumn,] <- genv[vfixcolumn,]
start           <- list("z" = z0, "v" = v0, "d" = d0, "b" = b0, "eta" = eta0, 
                        "zeta" = zeta0)
# MCMC
estim.ard1      <- mcmcARD(Y = ARD, traitARD = trait, start = start, fixv = vfixcolumn,
                           consb = bfixcolumn, iteration = 5000)  
```
```{r arda, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

********SUMMARY******** 
n              :  500 
K              :  12 
Dimension      :  3 
Iteration      :  5000 
Elapsed time   :  0  HH  1  mm  37  ss 
 
Average acceptance rate 
                      z:  0.441114 
                      d:  0.4399656 
                      b:  0.4408667 
                    eta:  0.4401833 
                   zeta:  0.4346")
```

```{r ardb, message=FALSE, eval=FALSE}
library(ggplot2)
data.plot1 <- data.frame(True_degree  = gend, 
                        Estim_degree = colMeans(tail(estim.ard1$simulations$d, 2500)))
ggplot(data = data.plot1, aes(x = True_degree, y = Estim_degree)) + 
   geom_abline(col = "red") + geom_point(col = "blue")
```
```{r ardbb, message=FALSE, echo=FALSE, fig.height = 3, fig.align = "center"}
library(ggplot2)
ggplot(data = data.plot1, aes(x = True_degree, y = Estim_degree)) + 
   geom_abline(col = "red") + geom_point(col = "blue")
```

```{r ard2a, eval=FALSE}
# Example2: ARD is observed for 70% population
# sample with ARD 
n          <- round(0.7*N)
# individual with ARD
iselect    <- sort(sample(1:N, n, replace = FALSE))
ARDs       <- ARD[iselect,]
traits     <- trait[iselect,]
# initialization 
d0         <- d0[iselect]; z0 <- z0[iselect,] 
start      <- list("z" = z0, "v" = v0, "d" = d0, "b" = b0, "eta" = eta0, "zeta" = zeta0)
# MCMC
estim.ard2 <- mcmcARD(Y = ARDs, traitARD = traits, start = start, fixv = vfixcolumn,
                      consb = bfixcolumn, iteration = 5000)  
```
```{r ardc, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

********SUMMARY******** 
n              :  350 
K              :  12 
Dimension      :  3 
Iteration      :  5000 
Elapsed time   :  0  HH  1  mm  19  ss 
 
Average acceptance rate 
                      z:  0.4406074 
                      d:  0.4398063 
                      b:  0.44005 
                    eta:  0.4391333 
                   zeta:  0.4444")
```
```{r ard2b, eval=FALSE}
# estimation for non ARD
# we need a logical vector indicating if the i-th element has ARD
hasARD      <- (1:N) %in% iselect
# we use the matrix of traits to estimate distance between individuals
estim.nard2 <- fit.dnetwork(estim.ard2, X = trait, obsARD = hasARD, m = 1) 
```
```{r ardd, echo=FALSE}
cat("ARD non observed on the entire population 
0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

Average link probabilities estimated 
Iteration             : 2500 
Elapsed time          : 0  HH  0  mm  14  ss ")
```
```{r arde, eval=FALSE}
# estimated degree
estd          <- estim.nard2$degree
data.plot2    <- data.frame(True_degree  = gend, 
                            Estim_degree = estd, 
                            Has_ARD      = ifelse(hasARD, "YES", "NO"))
ggplot(data = data.plot2, aes(x = True_degree, y = Estim_degree, colour = Has_ARD)) + 
  geom_abline(col = "red") + geom_point() 
```
```{r ardee, message=FALSE, echo=FALSE, fig.height = 3, fig.align = "center"}
ggplot(data = data.plot2, aes(x = True_degree, y = Estim_degree, colour = Has_ARD)) + 
  geom_abline(col = "red") + geom_point() 
```

## Estimating the SAR model with ARD
```{r Bayesard00, echo=FALSE}
load(url('https://github.com/ahoundetoungan/PartialNetwork/blob/master/datavignettes/out.lsp.rda?raw=true'))
```
```{r bayesard1, eval=FALSE}
library(PartialNetwork)
set.seed(123)
M             <- 50
N             <- rep(30, M)
genzeta       <- 3.5
mu            <- -1.35
sigma         <- 0.37
K             <- 12    # number of traits
P             <- 3     # Sphere dimension 
# In this loop, we generate data for the latent space model and 
# estimate the latent space model in the M sub-networks
estimates     <- list()
list.trait    <- list()
prior         <- list()
G0            <- list()
for (m in 1:M) {
  # ARD parameters
  # Generate z (spherical coordinates)
  genz    <- rvMF(N[m], rep(0,P))
  # Generate nu  from a Normal(mu, sigma^2) (The gregariousness)
  gennu   <- rnorm(N[m],mu,sigma)
  # compute degrees
  gend    <- N[m]*exp(gennu)*exp(mu+0.5*sigma^2)*exp(logCpvMF(P,0) - logCpvMF(P,genzeta))
  # Link probabilities
  Probabilities <- sim.dnetwork(gennu, gend, genzeta, genz) 
  prior[[m]]    <- Probabilities
  # Adjacency matrix
  G        <- sim.network(Probabilities)
  G0[[m]]  <- G
  # Generate vk, the trait location
  genv     <- rvMF(K, rep(0, P))
  # set fixed some vk  distant
  genv[1,] <- c(1, 0, 0)
  genv[2,] <- c(0, 1, 0)
  genv[3,] <- c(0, 0, 1)
  # eta, the intensity parameter
  geneta   <-abs(rnorm(K, 2, 1))
  # Build traits matrix
  densityatz       <- matrix(0, N[m], K)
  for(k in 1:K){
    densityatz[,k] <- dvMF(genz, genv[k,]*geneta[k])
  }
  trait            <- matrix(0, N[m], K)
  for(k in 1:K){
    tmp       <- exp(geneta[k] + logCpvMF(3, geneta[k]))
    trait[,k] <- runif(N[m], 0.5*tmp, tmp) < densityatz[,k]
  }
  list.trait[[m]]  <- trait
  # Build ADR
  ARD         <- G %*% trait
  # generate b
  genb        <- numeric(K)
  for(k in 1:K){
    genb[k]  <- sum(G[,trait[,k]==1])/sum(G) + 1e-8
  }
  
  # initialization 
  d0     <- gend; b0 <- exp(rnorm(K)); eta0 <- rep(1,K); zeta0 <- genzeta; 
  z0     <- matrix(rvMF(N[m], rep(0,P)), N[m]); v0 <- matrix(rvMF(K,rep(0, P)), K)
  # We should fix some vk and bk
  vfixcolumn      <- 1:5
  bfixcolumn      <- 1:8
  b0[bfixcolumn]  <- genb[bfixcolumn]
  v0[vfixcolumn,] <- genv[vfixcolumn,]
  start           <- list("z" = z0, "v" = v0, "d" = d0, "b" = b0, "eta" = eta0, 
                          "zeta" = zeta0)
  # MCMC
  estimates[[m]]  <- mcmcARD(Y = ARD, traitARD = trait, start = start, fixv = vfixcolumn, 
                             sim.d = FALSE, sim.zeta = FALSE, consb = bfixcolumn, 
                             iteration = 1000)
}
## Simulate X and y
# individual effects
beta          <- c(2,1,1.5) 
# contextual effects
gamma         <- c(5,-3) 
# endogenous effects
alpha         <- 0.4
# std-dev errors
se            <- 1
# covariates
X             <- cbind(rnorm(sum(N),0,5),rpois(sum(N),7))
# Normalise G0
G0norm        <- norm.network(G0)
# simulate dependent variable use an external package
y             <- CDatanet::simSARnet(~ X, contextual = TRUE, Glist = G0norm, 
                                     theta = c(alpha, beta, gamma, se))
y             <- y$y
# dataset
dataset       <- as.data.frame(cbind(y, X1 = X[,1], X2 = X[,2])) 
```
```{r bayesard2, eval=FALSE}
mlinks       <- list(model = "latent space", estimates = estimates)
out.lspa1    <- mcmcSAR(formula = y ~ X1 + X2, contextual = TRUE, G0.obs = "none", 
                        data = dataset, mlinks = mlinks, iteration = 2e4)
```
```{r ayesarda, echo=FALSE}
cat("0%   10   20   30   40   50   60   70   80   90   100%
[----|----|----|----|----|----|----|----|----|----|
**************************************************|

The program successfully executed 

*************SUMMARY************* 
Number of group        :  50 
Iteration              :  20000 
Elapsed time           :  3  HH  46  mm  59  ss 
 
Peer effects acceptance rate: 0.44765
rho acceptance rate         : 0.269653")
```

```{r Bayesard2a}
summary(out.lspa1) 
```
```{r Bayesard2b, fig.height = 3, fig.align = "center"}
plot(out.lspa1, plot.type = "sim", mar = c(3, 2.1, 1, 1))
```

